\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-30 appendix.qmd
Add notation table in the Appendix

@@

- Why bin means? because the distribution of points within hexagonals are not always reprsented by the center.

>>>>

| Notation                                                                                                              | Description                                                            |
|-----------------------------------------------------------------------------------------------------------------------|------------------------------------------------------------------------|
| $n$                                                                                                                   | number of observations                                                 |
| $p$                                                                                                                   | number of dimensions in high-D data                                    |
| $X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ | high-D data matrix                                                     |
| $d$                                                                                                                   | number of dimensions in embedding data, usually two                    |
| $Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ | embedding matrix                                                       |
| $P_t$                                                                                                                 | point along the geodesic path at time $t$                              |
| $P_{t+1}$                                                                                                             | point along the geodesic path at the next time instant, which is $t+1$ |
| $b_1$                                                                                                                 | number of bins along the x-axis                                        |
| $b_2$                                                                                                                 | number of bins along the y-axis                                        |
| $b$                                                                                                                   | total number of bins in the hexagonal grid                             |
| $b'$                                                                                                                  | total number of bins without the empty bins                            |
| $h$                                                                                                                   | diameter of a hexagon                                                  |
| $A$                                                                                                                   | area of a hexagon                                                      |
| $r_1$                                                                                                                 | 2D embedding component 1                                               |
| $r_2$                                                                                                                 | 2D embedding component 2                                               |
| $s$                                                                                                                   | shape parameter                                                        |
| $C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$                                                                               | hexagonal bin centroid coordinates                                     |
| $C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$                                                                          | averaged high-D coordinates                                            |
: Notations used in this paper and their descriptions. {#tbl-notations}

@@

- Why bin means? because the distribution of points within hexagonals are not always represented by the center.

### 2024-01-30 paper.tex
Add notation table in the Appendix

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, interior hidden, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable]}{\end{tcolorbox}}\fi
